### 2020-02-20 Writing/disparity_review.tex
updated all references

While studies of morphological disparity would benefit from advances in multidimensional analysis in other fields, the concept of a morphospace could reciprocally benefit other disciplines.
For example, the multidimensional analysis of Diaz \citealt{Diaz2016-mr}, which analysed patterns of form and function in plants, is essentially an ecomorphospace; isotopic analyses of organisms \citep{Jackson2011-kq} can be represented as an isotope-space; ecosystem functioning in \citealt{Donohue2013-bg} as an ecosystem-space, etc.
% AJ: this is a potential nice, although rather data hungry I believe, methods that I think could be worth dropping into the paper somewhere. Either here as a quick drop, or earlier up under overlap seems appropriate if you want to add it https://esajournals.onlinelibrary.wiley.com/doi/10.1890/14-0235.1
These generalisations could also be exported for any set of traits (e.g. acousto-spaces for acoustic traits or glotto-spaces for linguistic traits).
%SG: devising 
Cognate approaches have been adopted recently in the analysis of single cell comparative transcriptome data \href{https://paperpile.com/c/sTGYvp/856K}{(Sebé-Pedrós et al. 2018)} where interpretation of the resulting transcriptome-spaces would be improved by heeding the concerns we highlight concerning morphospaces.
% ES: Suggested by Erin: reword this sentence

Although disparity analyses are now simple to implement in freely available softwares \href{https://paperpile.com/c/sTGYvp/xDqf+J2G1+9JdS+9Zoi+bCsU+EmTR+2KmX}{(e.g., Guillerme 2018;} {; Bouxin 2005; Harmon et al. 2008; Lloyd 2016; Navarro 2003; Oksanen 2007)},
% @@@ add BAT
it is crucial to remember that they are multidimensional analyses and multidimensional analyses are complex.
We assert that future morphological analyses will benefit by emphasising the methodological decisions made, rather than simply using disparity analysis because \emph{we can}.

\hypertarget{author-contributions}{%
\section{5. Author contributions}\label{author-contributions}}

@@

\hypertarget{acknowledgments}{%
\section{6. Acknowledgments}\label{acknowledgments}}

>>>>

While studies of morphological disparity would benefit from advances in multidimensional analysis in other fields, the concept of a morphospace could reciprocally benefit other disciplines.
For example, the multidimensional analysis of Diaz \citealt{Diaz2016-mr}, which analysed patterns of form and function in plants, is essentially an ecomorphospace; isotopic analyses of organisms \citep{Jackson2011-kq} can be represented as an isotope-space; ecosystem functioning in \citealt{Donohue2013-bg} as an ecosystem-space, etc.
% AJ: this is a potential nice, although rather data hungry I believe, methods that I think could be worth dropping into the paper somewhere. Either here as a quick drop, or earlier up under overlap seems appropriate if you want to add it https://esajournals.onlinelibrary.wiley.com/doi/10.1890/14-0235.1
These generalisations could also be exported for any set of traits (e.g. acousto-spaces for acoustic traits or glotto-spaces for linguistic traits).
%SG: devising 
Cognate approaches have been adopted recently in the analysis of single cell comparative transcriptome data \citep{Sebe-Pedros2018-sw} where interpretation of the resulting transcriptome-spaces would be improved by heeding the concerns we highlight concerning morphospaces.
% ES: Suggested by Erin: reword this sentence

Although disparity analyses are now simple to implement in freely available softwares \citep{Navarro2003-vz, Bouxin2005-wk, oksanen2007vegan, Harmon2008-gq, lloyd2016, Guillerme2018-uc}.
it is crucial to remember that they are multidimensional analyses and multidimensional analyses are complex.
We assert that future morphological analyses will benefit by emphasising the methodological decisions made, rather than simply using disparity analysis because \textit{we can}.

\subsection{Author contributions}

@@

\subsection{Acknowledgments}
